A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-21 FMCAD2021/4_dec_proc.tex
space adjustment
Update 4_dec_proc.tex

Furthermore, as Point's procedure is quite expensive and a faithful implementation would not scale\footnote{We did implemented Point's algorithm and discovered that the implementation could only solve formulas of very small size.},
in the next section, we will propose various optimizations to Point's algorithm, aiming at an efficient implementation.

>>>>

Furthermore, as Point's procedure is quite expensive and a faithful implementation would not scale\footnote{We did implement Point's algorithm and discovered that the implementation could only solve formulas of very small size.},
in the next section, we will propose various optimizations to Point's algorithm, aiming at an efficient implementation.
